Flat histogram method comparison on 2D Ising Model

### 2020-04-17 ising/ising.tex
added some text to the paper.

Due to a canonical Monte Carlo simulation's inefficient sampling of large
energies, a variety of ``flat'' (or ``broad'') histogram
methods~\cite{penna1996broad, penna1998broad, swendsen1999transition,
wang2001determining, wang2001efficient} were developed to explore a wider range
of energies.  In addition to obtaining thermodynamic information for the entire
energy range for a single simulation, these approaches cannot be easily trapped
in a local energy minimum like a canonical simulation.

@@

\section{Conclusion}
We have examined the convergence of SAD versus other widely used weight-based
histogram methods.  We have shown that Sad samples the energy space
corresponding to a desired range of temperatures for a variety of system sizes.
We find that both SAD and 1/t-WL demonstrate excellent and robust convergence.
They both converge more rapidly than SAMC, and unlike WL do not suffer from
error saturation. We find that for larger systems SAD reduces the updated factor
more slowly (and conservatively) than 1/t-WL. This means that SAD will take
proportionately more moves to converge to the same value as 1/t-WL as system
size is increased. SAD requires the user to specify a temperature range of
interest rather than an energy range of interest as 1/t-WL does. For use cases
in which a range of desired temperatures is known, this will make the SAD method
considerably more convenient.

\bibliography{ising} % Produces the bibliography via BibTeX.

>>>>

Multicanonical methods, introduced by Berg and Neuhaus, enabled flat-histogram sampling which improved the exploration of configuration space and allowed the system to overcome free-energy barriers~\cite{berg1991multicanonical, berg1992multicanonical}.  These works led to increase in the development of a variety of ``flat'' (or ``broad'') histogram
methods~\cite{penna1996broad, penna1998broad, swendsen1999transition,
wang2001determining, wang2001efficient} which could explore a wider range
of energies.  In addition to obtaining thermodynamic information for the entire
energy range for a single simulation, these approaches cannot be easily trapped
in a local energy minimum like a canonical simulation.

@@

\section{Conclusion}
\jpsays{add something here about production run WL-minGamma}
We have examined the convergence of SAD versus other widely used weight-based
histogram methods.  We have shown that Sad samples the energy space
corresponding to a desired range of temperatures for a variety of system sizes.
We find that both SAD and 1/t-WL demonstrate excellent and robust convergence.
They both converge more rapidly than SAMC, and unlike WL do not suffer from
error saturation. We find that for larger systems SAD reduces the updated factor
more slowly (and conservatively) than 1/t-WL. This means that SAD will take
proportionately more moves to converge to the same value as 1/t-WL as system
size is increased. SAD requires the user to specify a temperature range of
interest rather than an energy range of interest as 1/t-WL does. For use cases
in which a range of desired temperatures is known, this will make the SAD method
considerably more convenient.

\section{Acknowledgments}
We thank Klas Markstr\"{o}m for discussions regarding the exact computation of the partition function for the 2D Ising model.

Johannes Zierenberg for production run discussions

Martin Weigel for talking about EPA could cite earlier.
\bibliography{ising} % Produces the bibliography via BibTeX.
